Multiproxy analysis exploring patterns of diet and disease in dental calculus and skeletal remains from a 19th century Dutch population

### 2023-09-20 README.Rmd
trigger render-readme action
update README and dependencies - issues during CODECHECK

@@

  - [:file\_folder: paper](/analysis/paper): Quarto source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis.
  - [:file\_folder: data](/data/): Data output from `data-raw/*.R`, used in the analysis (*.rda*).
  - [:file\_folder: analysis/figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.
  - [:file\_folder: R](/R/): R functions required in the analysis.
  - [:file\_folder: data-raw](/data-raw/): R script to download and process the raw data from Zenodo (https://zenodo.org/record/8061483).

@@

@@

You can download the compendium as a zip from from this URL:
[main.zip](/archive/main.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- finally, open `analysis/paper/paper.qmd` and **render** to produce the PDF manuscript (`_output/`),
  or run `rmarkdown::render("analysis/paper/paper.qmd")` in the R console.

>>>>

The **root** directory contains:

  - [:file\_folder: data-raw](/data-raw/): R script to download and process the raw data from Zenodo (https://zenodo.org/record/8061483).
  - [:file\_folder: data](/data/): Data output from `data-raw/*.R`, used in the analysis (*.rda*).
  - [:file\_folder: R](/R/): R functions required in the analysis.

@@

  - [:file\_folder: paper](/analysis/paper): Quarto source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.

@@

**If you are running Linux, you will need to install `gfortran`.**

e.g. `sudo apt install gfortran` for Ubuntu.

@@

You can download the compendium as a zip from from this URL:

[main.zip](/archive/refs/heads/main.zip).

or clone the repository:

`git clone git@github.com:bbartholdy/mb11CalculusPilot.git`

Then:

- open the `.Rproj` file in RStudio
- run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- finally, open `analysis/paper/paper.qmd` and **render** to produce the PDF manuscript (`_output/`),
  or run `quarto::quarto_render("analysis/paper/paper.qmd")` in the R console.

### 2023-09-20 analysis/paper/paper.tex
update README and dependencies - issues during CODECHECK

Keywords:  dental calculus; LC-MS/MS; alkaloids; dental pathology;
sinusitis; caffeine; tobacco 
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, sharp corners, interior hidden, frame hidden, breakable, enhanced]}{\end{tcolorbox}}\fi

>>>>

Keywords:  dental calculus; LC-MS/MS; alkaloids; dental pathology;
sinusitis; caffeine; tobacco 
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden, enhanced, interior hidden, breakable]}{\end{tcolorbox}}\fi
